Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-02 Paper.tex

Note that $\mindifficulty$ is the difficulty of the genesis block. The \textit{Homestead} difficulty parameter, $\homesteadmod$, is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below, as implemented in EIP-2 \cite{EIP-2}. In the Homestead release, the exponential difficulty symbol, $\expdiffsymb$ causes the difficulty to slowly increase (every 100,000 blocks) at an exponential rate, and thus increasing the block time difference, and putting time pressure on transitioning to proof-of-stake. This effect, known as the "difficulty bomb", or "ice age", was explained in EIP-649 \cite{EIP-649} and delayed and implemented earlier in EIP-2 \cite{EIP-2}. $\homesteadmod$ was also modified in EIP-100 with the use of $x$, the adjustment factor above, and the demoninator 9, in order to target the mean block time including uncle blocks \cite{EIP-100}. Finally, in the Byzantium release, with EIP-649, the ice age was delayed by creating a fake block number, $H'_{\mathrm{i}}$, which is obtained by substracting three million from the actual block number, which in other words reduced $\expdiffsymb$ and the time difference between blocks, in order to allow more time to develop proof-of-stake and preventing the network from "freezing" up.

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabu*}{X[l]X[c]X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements \cite{Davey2002_zbMATH01748069}.\\
\bottomrule
\end{tabu*}

>>>>

Note that $\mindifficulty$ is the difficulty of the genesis block. The \textit{Homestead} difficulty parameter, $\homesteadmod$, is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below, as implemented in EIP-2 by \cite{EIP-2}. In the Homestead release, the exponential difficulty symbol, $\expdiffsymb$ causes the difficulty to slowly increase (every 100,000 blocks) at an exponential rate, and thus increasing the block time difference, and putting time pressure on transitioning to proof-of-stake. This effect, known as the "difficulty bomb", or "ice age", was explained in EIP-649 by \cite{EIP-649} and delayed and implemented earlier in EIP-2. $\homesteadmod$ was also modified in EIP-100 with the use of $x$, the adjustment factor above, and the demoninator 9, in order to target the mean block time including uncle blocks by \cite{EIP-100}. Finally, in the Byzantium release, with EIP-649, the ice age was delayed by creating a fake block number, $H'_{\mathrm{i}}$, which is obtained by substracting three million from the actual block number, which in other words reduced $\expdiffsymb$ and the time difference between blocks, in order to allow more time to develop proof-of-stake and preventing the network from "freezing" up.

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabu*}{X[l]X[c]X} \savetabu{col3}
\toprule
Symbol & Latex Command & Description \hypertarget{bigvee}{}\\
\midrule
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{Davey2002_zbMATH01748069}).\\
\bottomrule
\end{tabu*}
